---
title: "Git and Github"
author: "Erika"
date: "2025-06-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Remember this:

```{r}
git config --global credential.helper manager
```


To enable Git Credential Manager (GCM) for Git on Windows, you should either install Git for Windows with the GCM component or install GCM separately as a standalone service. When using Git with HTTPS, GCM handles authentication by storing credentials in the Windows Credential Manager. 
Here's how to enable GCM:
1. Install Git for Windows with GCM (Recommended):
Download the latest Git for Windows installer from the Git website. 
During installation, ensure you select the "Git Credential Manager" option. 
This will install Git and automatically configure it to use GCM. 
2. Install GCM as a standalone service:
If you already have Git installed, you can download and install GCM separately from the Git Credential Manager for Windows repository. 
Follow the instructions on the repository to install it. 
You'll likely need to configure Git to use the GCM helper after installation. 
3. Configure Git to use GCM (if needed):
Open a Git Bash or command prompt.
Run the following command to configure Git to use the manager helper: 
Code

    git config --global credential.helper manager
 
4. Verify the configuration:
Run the following command to verify that the credential helper is set to "manager":
Code

    git config credential.helper
 
5. Using GCM:
When you perform Git operations that require authentication (e.g., git push, git clone over HTTPS), Git will automatically use GCM. 
GCM will present a graphical interface for you to authenticate, often using a browser window. 
Once you authenticate, GCM stores your credentials securely in the Windows Credential Manager. 
