---
title: "Git and Github"
author: "Erika"
date: "2025-06-23"
output: html_document
---

## Get started

Write some code here clear R's workspace and turn on the `tidyverse` suite of packages as well as the `here` package. Ask a friend or go back and look at some code from last week.

```{r}

```

## Pull in the data

Now write some code that pulls in the dataset called `AssignedSpecies_June2022.csv`. You might do it twice, once with `read.csv` and the next time with `read_csv` and see if you notice any differences (give each import a different name).

```{r}

```

## Use version control.
Let's stage and commit some changes together. Then let's push them to github

## Inspect our data
Last week, we learned about the `str()`, `glimpse()`, `unique()` and `levels()` functions for looking at our data.

Now let's try a few more:

Write some code that applies the function `head()` to your data.

```{r}

```

What happened?

Now write some code that applies the function `tail()` to your data. 

What happened?

## Use version control
Use what we did earlier to stage and commit changes.

## Summarise the dataset

Now write some code that applies the function `summary()` to your data.

```{r}

```

What did it do?

Can you use that same summary function and information you learned last week about the `$` to get a summary of a specific column of data?

```{r}

```

## Use version control
Go for it!