---
title: "Fitting-stats-model"
format: html
editor: visual
---

## Introduction

Two sessions ago, we worked with a data set of museum records for porcupines gathered from Arctos, a museum data base.

I have taken that data set and reduced it to the 90 rows of data that had complete information on a variety of locality, date, and body size measurement information for different animals. 

Today we will look at how we can use those data to fit a linear regression model.

Let's start by setting up our workspace and pulling in the data

```{r}
rm(list = ls())
library(tidyverse)
library(here)

porcs <- read_csv(here("Data/porcs_complete.csv"))
```
## Explore the data

We might imagine that their is a relationship between body mass and tail length (bigger, heavier animals might have longer tails...).  

Before we fit a model to check, let's get a feel for our data.



```{r}

summary(porcs$MASS_G) #examine continuous variable

ggplot(porcs, aes(MASS_G, fill = SEX))+
  geom_histogram()
```
Looks like we have an outlier!

Let's filter to animals with body mass less than 20000 g

```{r}
porcs <- porcs |>
  filter(MASS_G < 20000)
```

```{r}
ggplot(porcs, aes(MASS_G, fill = SEX))+
  geom_histogram()
```

Another way to view that plot:

```{r}
ggplot(porcs, aes(MASS_G, fill = SEX))+
  geom_histogram()+
  facet_wrap(~ SEX, ncol = 1)
```
Now look at tail length

```{r}

summary(porcs$TAIL_LENGTH_MM)

ggplot(porcs, aes(TAIL_LENGTH_MM, fill = SEX))+
  geom_histogram()+
  facet_wrap(~SEX, ncol = 1)
```
Looks ok.

## Plot the data and fit the model

Let's begin by making a plot of our data and determining what we expect our model to do.

```{r}
ggplot(porcs, aes(MASS_G, TAIL_LENGTH_MM))+
  geom_point() + #for scatter plots
  labs(x = "Body mass (g)", y = "Tail length (mm)")+ #axis labels
  theme_bw() #black and white basic plot theme
```
### Interpret the figure

It looks like the slope is positive. 

We can also guesstimate what the slope and intercept would be for this analysis:

Eyeballing the intercept, it might cross the y-axis at about 50 or so.
Eyeballing the slope, 
  - roughly speaking, the "rise" goes from a tail length of about 100 to a tail length of about 280. 280 minus 100 = 180
  - roughly speaking, the "run" spans from a body mass of 0 (??? - I can see it is actually 3.1 g above under the `summary` call - perhaps a typo or embryos?) to a body mass of 16,500. In other words, the "run" is about 16500.
  - "rise"/"run" thus is approx 180/16500 or 0.011.
  
### Fit the model
We use the `lm()` function to fit a linear regression.

```{r}
porc_model <- lm(TAIL_LENGTH_MM ~ MASS_G, data = porcs)
```

That's it!

How do we see the results???

(I'm skipping over an important step in a statistical analysis, which is that our data meet the assumptions for the chosen model.)

We use two tools: `anova()` and `summary()`.

`anova()` does not perform an ANOVA. Instead, it produces a classic anova table, the sums-of-squares table including the F-statistic, which is the ratio of variance explained by the explanatory variable to the leftover variance. As well, it produces an estimate of R^2 and adjusted R^2.

`summary()` is less confusing. It produces a table with the estimates of the coefficients of the line that is the model: an intercept and a slope.

Take a look:
```{r}
anova(porc_model)
```
```{r}
summary(porc_model)
```
So, it looks like there is a relationship between tail length and body mass. Can we get to a nicer figure?

```{r}
ggplot(porcs, aes(MASS_G, TAIL_LENGTH_MM))+
  geom_point() + #for scatter plots
  geom_smooth(method = "lm")+ #plot the regression line
  labs(x = "Body mass (g)", y = "Tail length (mm)")+ #axis labels
  theme_bw() #black and white basic plot theme
```




