---
title: "fixing-mistakes"
format: html
editor: visual
---

## Introduction

Set up the workspace
Turn on libraries
Read in trees.csv as data object called "trees"

```{r}
rm(list = ls()) #clear R's environment
library(tidyverse)
library(here)

trees <- read.csv(here("Data/trees.csv"))
```
Set up a statistical model

```{r}
tree.mod <- aov(DBH ~ Species, data = trees)
summary(tree.mod)
```
Take a look at our data!

```{r}
unique(trees$Species)
```
Let's fix the species column
Let's do the first one together: sugar maple

Use the `which` function and return row numbers that contain "sugar maple" as Species

```{r}
#option 1
bad_maples <- which(trees$Species == "sugar maple" | trees$Species == "maple")

#option2 uses %in%

 maples <- c("maple",  "sugar maple") 

 bad_maples2 <- which(trees$Species %in% maples)
 
 #option3 also uses %in%
 
 bad_maples3 <- which(trees$Species %in% c("maple", "sugar maple"))
```
Now we know which rows need to be repaired, so let's do it!

```{r}
trees$Species[bad_maples] <- "Sugar maple"
unique(trees$Species)
```

```{r}
fix_beech <- which(trees$Species == "Am. Beech" | trees$Species == "Beach")

trees$Species[fix_beech] <- "American beech"
unique(trees$Species)
```
```{r}
fix_birch <- which(trees$Species %in% c("Y. birch", "yellow birch"))

trees$Species[fix_birch] <- "Yellow birch"
unique(trees$Species)

```


```{r}
tree.mod <- aov(DBH ~ Species, data = trees)
summary(tree.mod)
```
```{r}
unique(trees$Site)
```
Look at continuous data

```{r}
ggplot(trees, aes(x = DBH, fill = Species)) +
  geom_histogram()
```

```{r}
which(trees$DBH > 48)
```










